Supporting Information

### 2021-10-08 Asymptomatic_LSR_Supplement_noPrisma_yesROB_HI.Rmd
Update Asymptomatic_LSR_Supplement_noPrisma_yesROB_HI.Rmd
DELETE

outbreakinv_rob_trafficlight <- rob_traffic_light(data = outbreakinv,
                                                           tool = "Generic",
                                                           psize = 10,
                                                           overall = FALSE)

p2 <- outbreakinv_rob_trafficlight +
  ggplot2::labs(
    caption = "  
    Domains:
  D1: Representativeness of the sample (selection bias)
  D2: Characteristics of non-respondents (selection bias)
  D3: Symptom assessment (information bias)
  D4: Recording of symptoms (information bias)
  D5: Classification of asymptomatic status (misclassification bias)
  D6: Selective reporting of symptoms status (attrition bias)")

p2 <- p2 + 
  ggplot2::ggtitle("Outbreak investigation")
p3 <- ggarrange(p1,p2,heights = c(1, 1.7), ncol = 1, nrow = 2)

@@

@@

![ROB Q1_1](q1_1_new.png)
![ROB Q1_1](q1_2_new.png)
![ROB Q1_1](q2_new.png)

>>>>

outbreakinv_rob_trafficlight <- rob_traffic_light(data = outbreakinv,
                                                           tool = "Generic",
                                                           psize = 10,
                                                           overall = FALSE)
p2 <- outbreakinv_rob_trafficlight +
  ggplot2::labs(
    caption = " ") + 
  ggplot2::ggtitle("Outbreak investigation") +
  ggplot2::theme(legend.position = "none")

p3 <- ggarrange(p1,p2,heights = c(1, 1.7), ncol = 1, nrow = 2)

p3 <- annotate_figure(p3, top = text_grob("Question 1", 
                                      color = "black", face = "bold", size = 21))

@@

dev.new()
png("q1_2_new.png", width = 1400, height = 2200)
p7
graphics.off()

@@

![ROB Q1_1](q1_1_new.png)
![ROB Q1_1](q1_2_new.png)
